Co-methylation

### 2015-04-21 Rmarkdown/comethylation.Rmd
Remove CGI abbreviation.

[^hepg2]: The minor exception is the _HepG2\_cell\_line_ where the CGI and non-CGI lines intersect by $IPD = 1500$, but we have already seen that this sample has an unusual methylome compared to the other samples.

@@

[^hepg2_2]: Again, the minor exception is the _HepG2\_cell\_line_ where the CGI and non-CGI distributions approximately overlap by $IPD = 50$, but we have already seen that this sample has an unusual methylome compared to the other samples.

@@

The Mantel-Haenszel estimator is an estimator of the common odds ratio for $2 \times 2 \times K$ tables. Therefore, using the MH estimator requires the assumption that all $2 \times 2$ tables have the same underlying odds ratio. The strata for co-methylation would be 'sample', 'IPD' and possibly 'region', where region is something like 'UMRs, LMRs, PMRs and other' or 'CGI and non-CGI'.

>>>>

[^hepg2]: The minor exception is the _HepG2\_cell\_line_ where the CpG island and non-island lines intersect by $IPD = 1500$, but we have already seen that this sample has an unusual methylome compared to the other samples.

@@

[^hepg2_2]: Again, the minor exception is the _HepG2\_cell\_line_ where the CpG island and non-island distributions approximately overlap by $IPD = 50$, but we have already seen that this sample has an unusual methylome compared to the other samples.

@@

The Mantel-Haenszel estimator is an estimator of the common odds ratio for $2 \times 2 \times K$ tables. Therefore, using the MH estimator requires the assumption that all $2 \times 2$ tables have the same underlying odds ratio. The strata for co-methylation would be 'sample', 'IPD' and possibly 'region', where region is something like 'UMRs, LMRs, PMRs and other' or 'CpG island and non-island'.
